\section{Discussion}
\label{sec:discussion}

\subsection{Multi-task interference impedes the grokking transition}

The headline empirical contribution of this paper is that joint
training on addition, subtraction, and multiplication mod $p$
\emph{qualitatively changes} the dynamics of grokking. Single-task
grokking on each of the three operations is sharp: train loss
collapses fast, test loss plateaus at the random-guess level, then
collapses through the grok step within a small fraction of the
training budget. The two-task experiment ($+$ and $-$) preserves the
sharp transition, and even slightly accelerates it relative to the
single-task baselines. The three-task experiment ($+$, $-$, $\times$)
loses the sharp transition entirely: instead of a plateau-then-collapse
shape, the test accuracy rises smoothly through 75{,}000 training
steps, reaching $0.60 / 0.48 / 0.32$ on the three tasks but never
crossing the 0.95 grok threshold within budget.

We do not have a complete mechanistic story for the slow ramp, but the
ingredients we do have are:
\begin{enumerate}
\item The two additive operations live on the cyclic group $\Z/p\Z$
      while multiplication lives on $(\Z/p\Z)^*$, a different cyclic
      group of different order. A model that solves all three tasks
      with Fourier features must therefore commit residual-stream
      capacity to two distinct bases.
\item Under aggressive weight decay, the implicit bias of the
      optimiser is toward small-Frobenius-norm representations, which
      makes the network prefer the smallest feature set that fits the
      training data. The two-basis solution costs more capacity than
      the one-basis solution required by single-task or two-task
      training.
\item The smooth ramp is consistent with a slow reorganisation
      between competing basis hypotheses, rather than the discrete
      jump from memorisation to a single Fourier algorithm seen in
      Nanda's setting.
\end{enumerate}

\subsection{Single-task replication: a sanity check}

The single-task replications (addition, subtraction, multiplication)
all groked cleanly at the published Nanda 2023 hyperparameters,
within a 5,000--7,500-step grok window. Multiplication groked
\emph{earliest} at this seed --- contrary to the published intuition
that multiplication is hardest --- but the qualitative picture
(memorisation $\to$ plateau $\to$ abrupt generalisation) is
preserved. The Fourier analysis in Section \ref{sec:analysis}
confirms that each model concentrates its embedding power in the
basis appropriate to its group operation, with sparse and clean
support.

\subsection{Limitations}

\paragraph{Step budget.}
The three-task experiment was run for 75{,}000 steps, which is
$\sim$10$\times$ the single-task grok step but evidently not enough
for the three-task model to fully grok. We do not yet know whether
extending to $200{,}000+$ steps would push the model through a
delayed grokking transition, or whether the slow-ramp dynamic
saturates without ever sharply transitioning. This is the most
important follow-up.

\paragraph{Curriculum and seed sweep.}
A curriculum experiment (warm-start from a grokked addition
checkpoint, then introduce the other two tasks) and a second
random seed for the three-task experiment were scheduled but not run
on the laptop hardware used for the present results. The
checkpoints from the first eight runs are released so these
experiments can be picked up on a CUDA box without redoing earlier
work.

\paragraph{One prime, one architecture.}
All experiments use $p = 113$ and the one-layer transformer of
\citet{nanda2023progress}. The robustness sweep checks $p \in
\{59, 113, 199\}$ and train fractions $\{0.30, 0.40, 0.50\}$ for the
single-task addition baseline; we do not run the multi-task variant
at multiple primes.

\paragraph{Mid-training Fourier analysis.}
The Fourier feature-overlap metric (Figure
\ref{fig:fig8_feature_overlap}) compares the multi-task model's
spectrum to each single-task spectrum at the partially-grokked
checkpoint. Both spectra are diffuse at this horizon, which makes the
cosine-similarity numbers hard to interpret directly. A fully-grokked
multi-task checkpoint would let us replace this metric with a
sharper subspace-overlap analysis.

\subsection{Relation to prior work}

Our single-task results extend the mechanistic story of
\citet{nanda2023progress} to subtraction and multiplication, with the
expected basis-by-group result. The multi-task slow-ramp finding is,
to our knowledge, novel: \citet{power2022grokking} demonstrate
grokking across a family of synthetic tasks but treat each in
isolation; \citet{nanda2023progress} restricts mechanistic analysis to
single-task addition; \citet{liu2022omnigrok,liu2022understanding}
develop effective theories of single-task grokking dynamics under
weight decay. The interference dynamic we report points at a possible
mechanistic boundary between sharp-transition and smooth-ramp regimes
that is set by how many distinct algorithms must coexist in a single
residual stream.

The slingshot mechanism of \citet{thilak2022slingshot} predicts that
adaptive optimisers can produce sudden generalisation transitions for
reasons unrelated to weight decay. The slow-ramp dynamic we observe
under the same optimiser settings ($\beta_2 = 0.98$) suggests that
slingshot dynamics, where they occur, are not strong enough to push
the multi-task three model through to grokking within 75{,}000 steps.
